### 2013-04-10 MSteenhagen-CV.tex
Reform. Heyth. RA description
Further refomulations of teaching experience

\ind 2009--Present. Research Assistant in Philosophy\\ (Philosophy of psychology, Clinical methodology, Psychoanalysis)

@@

\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art (Aesthetics)

@@

\ind 2011-2012. Teaching Assistant in Philosophy (Applied Ethics)

>>>>

\ind 2009--Present. Research Assistant in Philosophy, working on philosophy of psychology, clinical methodology and psychoanalysis.

@@

\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art, seminar leader and lecturer in aesthetics)

@@

\ind 2011-2012. Teaching Assistant in Philosophy, seminar leader applied ethics
